\section{Outlook}

In this paper, we highlighted the enormous impact of web ontologies itself and the capabilities of web ontologies in combination with Java Application. We analyzed several existing approaches for technically supporting such integration. From the perspective of integration as well as from a broader view of a modest installation web ontologies fail to keep promise of an overall flexible environment in style of MEAN stack software bundle. Although, it shares the same implementation steps as relational database services (MySQL) in Java Application the effort is pretty high to connect OWL to Java Application. Moreover, the amount available use cases and best practice approaches is still limited. This is due to the fact, that Web Semantic is as yet less popular inside the communities and this therefore needs to be further incentivized to raise popularity. A possibility can be the use of D2R Server. D2R Server allow to publish the content of relational databases on the Semantic Web in which it maps databases into RDF format.\\ 

There is thus a clear need for developing appropriate mechanisms to connect Java Application to OWL Files andto unleash the full potential of web ontologies. For further research, it would be interesting to work with Python, as a programming language with less leverage. Furthermore, it would be intressting to do a benchmarking between Java and Python in regard to OWL Files. Nevertheless,  Web Ontologies will become more and more important. With the emerge of Open Data Government policies, that allow free access to machine readable information, web semantic technologies like for instance RDF will play an important role in the future in scraping and linking data.

\newpage